\subsection{Potential Experiment}

\subsubsection{HowTo100M}

Given that the pretrained model does not work well for video-text retrieval on EpicKitchen dataset, we investigate a couple aspects:
\begin{itemize}
    \item Our use of HowTo100M is different from its original use: the model wants to retrieve the corresponding caption for a given video segment, and the caption is usually a descriptive sentence that reflects the video content. The training loss also reflects that there is only one positive within a batch, namely video-text pair $(\mathbf{v}_i, \mathbf{c}_i)$ that share the same index $i$. This is problematic for us since we want all $\mathbf{c}_i$ and all $\mathbf{v}_j$ corresponding to the same action to be close together irrespective of their indices in the batch. 
    
    Therefore, we can try to train with triplet loss that is computed based on the action labels $l \in \{0,\dots,96\}$. In a given batch of size $N$, there is a total of $2N^3$ triplets. 
    The first type of $(i,j,k)$ is $\mathbf{c}_i$, $\mathbf{v}_j$, $\mathbf{c}_k$, where given $\mathbf{v}_j$, $\mathbf{c}_i$ is the positive text, and $\mathbf{c}_k$ is the negative text.
    The second type of $(i,j,k)$ is $\mathbf{c}_i$, $\mathbf{v}_j$, $\mathbf{v}_k$, where given $\mathbf{c}_i$, $\mathbf{v}_j$ is the positive video, and $\mathbf{v}_k$ is the negative video. 
    We need to mask out pairs where 1) $l_i \neq l_j$ 2) $l_i = l_k$ 3) $i == j$.   
    
    \item One hypothesis is that $6144$ is too large of an embedding space for our limited text input. However, how limited is our text input compared to YouCook2? 
    
    \item By looking at the top-10 retrieved texts for a given video of YouCook2, which is also a cooking-based video dataset and whose domain is the closest to ours, we find that the captions are also a set of verbs and nouns, although they are much longer and comprise several actions. In comparison, our segment contains only one action and one pair of verb-noun in the phrase. 
    
    Therefore, another potential experiment is to combine several segments together so that we have a longer caption with multiple action verbs and nouns. In this way, we hope to replicate the YouCook2 results after finetuning.  
\end{itemize}